How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-27 Manuscript.tex
Updates from ShareLaTeX

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). 
   \fig{bdbc} shows an example of a feature model defining valid combinations of settings to on the
   the Siegmund et al. datasets. These feature models were used by Siegmund et al. to ensure all their perturbations are value
   (we will use the same models to cull invalid plans).
  Given those valid perturbations, the systems were then compiled and 
  Siegmund et al. recorded how long each perturbation took to run a test suite.

@@

 \input{tex/algos}
\subsubsection{Method3= BIC=   Method2 + Best-in-cluster}\label{sect:BIC}

@@

Method3 connects  each centroid to a nearest neighbor
by a {\em gradient}.
Each gradient has a (bottom,top) end labelled  ($C_i,C_j$) containing the  (worst,best) centroid performance scores, respectively..  
For each test instance, Method3 
find the nearest gradient, the runs up to the top  best end $C_j$, then extracts $B_j$ (which is the
 best-in-cluster associated with  $C_j$).
The returned plan is then computed  from the delta between the test case
and $B_j$.

@@

 \begin{figure}[!h]
{\small 
\[
\begin{array}{r} 
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; XTREE)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{before}& =\mathrm{Performance\; scores \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{before} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} R=\frac{\mathit{after}}{\mathit{before}}
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]}
 \caption{Experimental design .}\label{fig:design}
 \end{figure}

@@

Else, we (1)~apply the { planner} to alter the {\em test} data;
then (2)~apply the { predictor} to the altered data $test'$;
then (3)~return data on the {\em before, after} predictions expressed as the ratio $R=\frac{\mathit{after}}{\mathit{before}}$.
This is a unit-less ratio with the following properties:
\bi
\item If $R= 1$, this means  ``no change from baseline''; 
\item If $R < 1$, this indicates ``some reduction to the baseline'';
\item If $R > 1$, this indicates ``optimization failure''.
\ei
 \subsubsection{Statistical Methods}
 Our methods use some stochastic algorithms; e.g. WHERE's selection of ``what example to explore first'' (see \fig{where}.C) and
  XTREE' occasional use of a random guess when deciding what part of a discretized range to include in the plan
  (see \fig{xtrees_bare}). Hence, we report the $R$ values seen in 40 repeated runs
  (with different random number seeds).
The the value 40 was chosen to be  larger than the 30 samples  required
to satisfy the central limit theorem.

@@

{\small  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~}c@{}r}} 
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
1 &         XTREE &    0.49  &  0.13 & \quart{7}{25}{17}{115} \\\hline  
2 &      CD &    0.59  &  0.18 & \quart{15}{34}{36}{115} \\
2 &          BIC &    0.60  &  0.12 & \quart{24}{24}{38}{115} \\\hline  
3 &      CD+FS &    0.62  &  0.06 & \quart{36}{12}{42}{115}  \\\hline \end{tabular}}
\end{center}

In this example table, the rows are  sorted on the median values of each method. Note that all the methods
have   $R<1$ values; i.e. all these methods reduced the expected value of the performance score in that experiment
while XTREE achieved the greatest reduction (down to 49\% of the original value).

@@

\fig{jur} and \fig{conf1} show the effectiveness of our methods seen in 40 repeats with each data set.
In these experiments,   the dependent variables of Jureczko and Siegmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Siegmund data.
\bi
\item For Siegmund data, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data. 
\item For the Jureczko data, we used the training and testing sets of \fig{j}. For these datasets,
 all the SMOTE-ing and Random Forest tunings (discussed in \tion{tesd})
occurred in the {\em train} phase of \fig{design}.
\ei
 \subsection{Experimental Results}

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method4 (XTREE) assumed that another sibling was useful if  had 
 a  score less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei

>>>>

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). Then, the performance was measured using standard benchmarking tools (delivered by \textsc{Oracle} for Berkley data sets and other popular tools such as \textsc{autobench} and \textsc{httpref})~\cite{sven12}. It's worth noting that in each of the above data set, some configurations are interdependent, this is expressed using a \textit{feature model}.
   \fig{bdbc} shows an example of such a feature model defining valid combinations of settings to on the Berkley database (``C'' version). These feature models were used by Siegmund et al. to ensure all their perturbations are valid
   (we will use the same models to cull invalid plans).

@@

 \input{tex/algos}
\subsubsection{Method3= GD=   Method2 + Gradient}\label{sect:BIC}

@@

Method3 connects  each centroid to a nearest neighbor
by a {\em gradient}.
Each gradient has a (bottom,top) end labelled  ($C_i,C_j$) containing the  (worst,best) centroid performance scores, respectively..  
For each test instance, Method3 
find the nearest gradient, the runs up to the top  best end $C_j$, then extracts $B_j$ (which is the
 best-in-cluster associated with  $C_j$).
The returned plan is then computed as a fraction of the gradient between the test case
and $B_j$.

@@

 \begin{figure}[!h]
{\small 
\[
\begin{array}{r} 
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; XTREE)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{before}& =\mathrm{Performance\; scores \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{before} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} R=(1-\frac{\mathit{after}}{\mathit{before}})\times 100 \%
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]}
 \caption{Experimental design .}\label{fig:design}
 \end{figure}

@@

Else, we (1)~apply the { planner} to alter the {\em test} data;
then (2)~apply the { predictor} to the altered data $test'$;
then (3)~return data on the {\em before, after} predictions expressed as percent improvement $R=(1-\frac{\mathit{after}}{\mathit{before}})\times100\%$ with the following following properties:
\bi
\item If $R= 0\%$, this means  ``no change from baseline''; 
\item If $R < 0\%$, this indicates ``some reduction to the baseline'';
\item If $R > 0\%$, this indicates ``optimization failure''.
\ei
 \subsubsection{Statistical Methods}
 Our methods use some stochastic algorithms; e.g. WHERE's selection of ``what example to explore first'' (see \fig{where}.C) and
  XTREE' occasional use of a random guess when deciding what part of a discretized range to include in the plan
  (see \fig{xtrees_bare}). Hence, we report the $R$ values seen in 40 repeated runs
  (with different random number seeds).
The the value 40 was chosen to be  larger than the 30 samples  required
to satisfy the central limit theorem.

@@

{\small  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~}c@{}r}} 
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
1 &         CD+FS &    49  &  13 & \quart{7}{25}{17}{115} \\\hline  
2 &      CD &    59  &  18 & \quart{15}{34}{36}{115} \\
2 &          BIC &    60  &  12 & \quart{24}{24}{38}{115} \\\hline  
3 &      XTREE &    62  &  6 & \quart{36}{12}{42}{115}  \\\hline \end{tabular}}
\end{center}

In this example table, the rows are  sorted on the median values of each method. Note that all the methods
have   $R<0\%$ values; i.e. all these methods reduced the expected value of the performance score in that experiment
while XTREE achieved the greatest reduction (of 60\% from the original value).

@@

\fig{jur} and \fig{conf1} show the effectiveness of our methods seen in 40 repeats with each data set.
In these experiments,   the dependent variables of Jureczko and Siegmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Siegmund data.
\bi
\item For Siegmund data, we performed a k-fold cross validation. Given the relatively smaller sample sizes in Apache and BDBJ, we chose $k=2$. This, we reasoned, would maintain a sufficiently large test data size in order for R to be measured reliably. However, in 2-fold cross validation, the division of data tends to affect the outcome significantly. To counter this, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data, repeating the process 40 times as mentioned above.
\item For the Jureczko data, we used the training and testing sets of \fig{j}. For these datasets,
 all the SMOTE-ing and Random Forest tunings (discussed in \tion{tesd})
occurred in the {\em train} phase of \fig{design}.
\ei
 \subsection{Experimental Results}

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method3 uses a fraction $F=0.5$ to compute the plan from the delta;
\item Method4 (XTREE) assumed that another sibling was useful if  had 
 a  score less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei

### 2015-08-27 tex/results_models.tex
Updates from ShareLaTeX

\begin{figure}[!t]

~\hrule~

%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &        XTREE &    0.42  &  0.17 & \quart{0}{10}{0}{20} \\
\hline  2 &      CD+FS &    1.03  &  0.69 & \quart{30}{46}{42}{20} \\
  2 &          BIC &    1.04  &  0.01 & \quart{42}{0}{42}{20} \\
  2 &      CD &    1.11  &  1.24 & \quart{18}{80}{46}{20} \\
\hline 
\end{tabular}}

 ~\hrule~
\caption{Results: Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data.
}\label{fig:coc}
\end{figure}

>>>>

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &          HOW &    -3.3  &  2.2 & \quart{26}{2}{27}{32} \\
  1 &      baseln0 &    -2.9  &  11.7 & \quart{17}{14}{28}{32} \\
  1 &      baseln1 &    -2.75  &  65.5 & \quart{0}{78}{28}{32} \\
\hline  2 &        dtree &    51.5  &  14.84 & \quart{82}{17}{93}{32} \\
\end{tabular}}
\caption{Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when other planners fail to do so.
}\label{fig:coc}
\end{figure}
